A meta-analysis of mental rotation ability in the first years of life

### 2022-04-26 code/analysis.Rmd
Re-format study table

```{r, tab_within}
# Helper functions to re-format age in years and/or months
format_days_years <- function(days) {
  days_per_year <- 365.25
  days_per_month <- 30.417
  years <- days %/% days_per_year
  months <- round((days - years * days_per_year) / days_per_month)
  str <- paste0(as.character(years), "y ", as.character(months), "m")
  str[is.na(days)] <- NA
  return(str)
}
format_days_months <- function(days, digits = 1) {
  days_per_month <- 30.417
  months <- days / days_per_month
  str <- format(round(months, digits), trim = TRUE, nsmall = digits)
  str <- paste0(str, "m")
  str[is.na(days)] <- NA
  return(str)
}

# Save within-analysis table of experiments
dat %>%
  transmute(
    Article = if_else(article == lag(article, default = ""), "", article),
    Experiment = group_long,
    `Sample size` = sample_size,
    `Females` = round(female_percent * sample_size),
    `Mean age^a` = format_days_years(age_mean),
    SD = format_days_months(age_sd),
    Task = task,
    `Stimulus type` = str_to_sentence(stimuli_presentation),
    `Stimulus dimensions` = stimuli_dimensions
  ) %>%
  print(n = Inf)
write_csv(
  file = here(tables_dir, "within_experiments.csv"),
  na = "n/a"
)
```

>>>>

```{r, tab_within}
# Helper functions to re-format age in years and/or months
format_days_months <- function(days) {
  days_per_month <- 30.417
  months <- days %/% days_per_month
  days_left <- round(days - months * days_per_month)
  str <- paste0(as.character(months), "m ", as.character(days_left), "d")
  str[is.na(days)] <- NA
  return(str)
}

# Save within-analysis table of experiments
dat %>%
  mutate(
    age_mean = format_days_months(age_mean),
    age_sd = str_c(as.character(round(age_sd)), "d"),
  ) %>%
  transmute(
    Article = if_else(article == lag(article, default = ""), "", article),
    Experiment = group_long,
    `Sample size` = sample_size,
    `Females` = round(female_percent * sample_size),
    Age = str_c(age_mean, "±", age_sd, sep = " "),
    Task = task,
    `Stimulus type` = str_to_sentence(stimuli_presentation),
    `Stimulus dimensions` = stimuli_dimensions
  ) %>%
write_csv(
  file = here(tables_dir, "within_experiments.csv"),
  na = "n/a"
)
```
